Kronos \& Krios: TBD

### 2017-05-29 paper/ms.tex
Take care of minor todos and update planets for HD20782/1

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:kk}.

@@

\todo{Figure: posterior distributions of separation and delta V}

@@

The element \elem{Li} is worth a special attention in the context of accretion scenario.
Because Li is present in either carbonaceous chondrites or the bulk Earth with
a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
but is depleted over time on the surface of a Sun-like star, accretion of
either at later time will significantly replenish the lithium on the star's
surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material results in $\Delta\elemH{Li} \approx 1.6$~dex.
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ().
Thus, as long as we believe the Sun's present-day surface Li abundance
to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
in its Li.
This is in fact exactly what we find: the Li abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \todo{CITE JM?})
approximately $1.6$~dex higher than the solar value of $1.1$~dex.
Furthermore, this implies that the accretion event should have happened
very recently from a time ago that is shorter than the \elem{Li} depletion time.

@@

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (corresponding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$).
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.

>>>>

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164-7799$~\AA.
Typical signal-to-noise ratio in continuum is $>200$~per pixel.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:kk}.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.

@@

@@

The element \elem{Li} is worth a special attention in the context of accretion scenario.
Because Li is present in either carbonaceous chondrites or the bulk Earth with
a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
but is depleted over time on the surface of a Sun-like star, accretion of
either at later time will significantly replenish the lithium on the star's
surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material results in $\Delta\elemH{Li} \approx 1.6$~dex.
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ().
Thus, as long as we believe the Sun's present-day surface Li abundance
to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
in its Li.
This is in fact exactly what we find: the Li abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:kk}, \citealt{jmlithium})
approximately $1.6$~dex higher than the solar value of $1.1$~dex.
Furthermore, this implies that the accretion event should have happened
very recently from a time ago that is shorter than the \elem{Li} depletion time.

@@

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (corresponding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$)
\footnote{The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{} that HD~20781 hosts four planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\
  with $e \le 0.11$ within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.
